The not so widening achievement gap: an interntational comparison of the evolution of the SES achievement gap from 2000-2015

### 2017-08-25 paper/paper.Rnw
Added posterior checks for cumulative difference model - model sucks but at least we know it

replication %>%
  enframe() %>%
  unnest() %>%
  qplot(minus_sample, geom = "histogram", data = .)

replication %>%
  enframe() %>%
  unnest() %>%
  summarize(mean(between(minus_sample, -0.05, 0.05)))

@@

# What happened if you adjut the trend splines for the tracking data?
@

@@

ready_data_two <-
  ready_data %>%
  group_by(country) %>%
  summarize(
    cum_diff = sum(difference, na.rm = TRUE),
    length = unique(length),
    num_tracks = unique(num_tracks),
    age_selection = unique(age_selection),
    central_examination = unique(central_examination),
    avg_track = unique(ztrack)
         )

# mod_tracking <-
#   ready_data_two %>%
#   lm(cum_diff ~ age_selection, data = .)

mod_tracking <-
  ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  stan_glm(cum_diff ~ age_selection, data = .,
           family = "gaussian",
           prior = normal(0, 2),
           prior_intercept = normal(0, 5),
           prior_aux = cauchy(0, 1),
           refresh = -1)

ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  mutate(pred_mean = posterior_predict(mod_tracking) %>% colMeans(),
         pred_median = posterior_predict(mod_tracking) %>% colMedians()) %>%
  select(country, cum_diff, pred_mean, pred_median) %>%
  gather(cat, value, -country) %>%
  ggplot(aes(country, value, fill = cat)) +
  geom_col(position = "dodge") +
  coord_flip()

>>>>

replication %>%
  enframe() %>%
  unnest() %>%
  qplot(perc_sample, geom = "histogram", data = .)

replication %>%
  enframe() %>%
  unnest() %>%
  summarize(mean(perc_sample < 0.5))

@@

@@

vars_unique <- c("length", "num_tracks", "age_selection", "central_examination", "ztrack")

ready_data_two <-
  ready_data %>%
  group_by(country) %>%
  summarize_at(vars(vars_unique), unique) %>%
  mutate(cum_diff = ready_data %>% group_by(country) %>% summarize(m = sum(difference)) %>% pull(m))

mod_tracking <-
  ready_data_two %>%
  lm(cum_diff ~ num_tracks + age_selection, data = .) %>%
  arm::display()

mod_tracking <-
  ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  brm(
    cum_diff ~ age_selection,
    family = gaussian(),
    data = .,
    prior = set_prior("cauchy(13, 1)", coef = "age_selection"),
    warmup = 1000, iter = 2000, chains = 5
  )

replication <-
  map(1:2000, ~ {
  ready_data_two %>%
  mutate(pred_sample = y_rep[sample(1:4000, 1), , drop = TRUE]) %>%
  summarize(perc_sample = mean(pred_sample > cum_diff),
            minus_sample = mean(pred_sample - cum_diff))
})

y_pred_data <-
  replication %>%
  enframe() %>%
  unnest()

y_pred_data %>% qplot(perc_sample, data = ., geom = "histogram", bins = 50)

y_pred_data %>% {quantile(.$perc_sample)}

y_pred_data %>%
  summarize(mean_perc = mean(perc_sample < 0.5))

bayes_R2(mod_tracking)

# Too few data points to predict integers, the distribution is full of empty spaces
# The predictions are too wide! Only 41% of the predictions are between 0.45 and 0.55
# accuracy. There's more underprediction than over prediction

ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  mutate(pred_median = posterior_predict(mod_tracking) %>% colMedians()) %>%
  select(country, cum_diff, pred_median) %>%
  gather(cat, value, -country) %>%
  ggplot(aes(country, value, fill = cat)) +
  geom_col(position = "dodge") +
  coord_flip()
@
